\sysfull

### 2017-08-11 paper/evaluation.tex
work on evaluation section

The applications that were used in the evaluation are: (i) \textbf{Bitcount}: counts bits in x y byte pseudo-random string using x algorithms. Each result is compared for correctness; (ii) \textbf{Cold chain}: emulates embedded temperature sensing engine: measurements are randomly generated and are compressed using LZW algorithm for x-entry dictionary and y-byte block; (iii) \textbf{Cuckoo}: implements cuckoo filter---x entry filter filled to y of capacity---program first stores a sequence of pseudo-random numbers, then queries the filter to recover it; (iv) \textbf{RSA}: encrypts predefined x byte long string with a y bytes long key\todo{were keys of 64 bytes tested? If yes: d they exhaust energy}{Amjad}. This set of benchmarks is the same as used in~\cite{chain,alpaca}\todo{Fill-in the missing data and verify its correctness}{Przemek/Amjad}. In addition to Chain benchmarks new applications were implemented: (v) \textbf{DFT}, (vi) \textbf{Huffman compressor}, and (vii) \textbf{Selection Sort}. All applications are compared in Table~\ref{table:benchmark_list} in terms of source lines of code against Chain. \todo{finalize describing all applications once all experiments are done}{Przemek}

@@

We start with evaluating the efficiency of a \sys compiler. Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging calls in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%. The result indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer alias. Thus, it results in \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provide in Section~\ref{}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise compiler can be used to simplify the programmability.

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile DFT application since the LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1GB memory that has Arch Linux, running on Intel Core i5-6200U (2.30GHz) processor. The result are given in Table~\ref{table:compile_time}. We simply used {\em date} command provided by linux to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live range of each variables. Apps such as RSA whose code size is large and uses a lot of variables needed longer compilation time due to larger search space for pointer aliasing.

>>>>

The applications that were used in the evaluation are: (i) \textbf{Bitcount}: counts bits in byte pseudo-random string using varying algorithms. Each result is compared for correctness; (ii) \textbf{Cold chain}: emulates an embedded temperature sensing engine: measurements are randomly generated and are compressed using a LZW algorithm for x-entry dictionary and y-byte block; (iii) \textbf{Cuckoo}: implements cuckoo filter---x entry filter filled to y of capacity---the program first stores a sequence of pseudo-random numbers, then queries the filter to recover it; (iv) \textbf{RSA}: encrypts predefined x byte long string with a y bytes long key\todo{were keys of 64 bytes tested? If yes: do they exhaust energy}{Amjad}. This set of benchmarks is the same as used in~\cite{chain,alpaca}\todo{Fill-in the missing data and verify its correctness}{Przemek/Amjad}. In addition to Chain benchmarks new applications were implemented: (v) \textbf{DFT}, (vi) \textbf{Huffman compressor}, and (vii) \textbf{Selection Sort}. All applications are compared in Table~\ref{table:benchmark_list} in terms of source lines of code against Chain.

@@

We start with evaluating the efficiency of the \sys compiler Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging calls\todo{calls or code? what is paging call?}{Kiwan} in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%\todo{except for cc and ar---why?}{Kiwan}. The result indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, the \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer aliasing. Thus, it results in the \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provided in Section~\ref{sec:result_compiler_time}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise the compiler can be used to simplify the programmability.

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile DFT application since the LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1\,GB memory with Arch Linux, running on Intel Core i5-6200U (2.30\,GHz) processor. The result are given in Table~\ref{table:compile_time}. We used a {\em date}\todo{date or time?}{Kiwan} linux command to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live ranges of variables. Apps such as RSA whose code size is large and uses a lot of variables, need longer compilation time due to a larger search space for pointer aliasing.
